\chapter{Introduction}

The development and functioning of a cell and an organism in general is a product of a complex cellular machinery. This machinery is compound by the interaction of genes, proteins, mRNA and many other substances to induce a cascade of extracellular signals transducted by mechanisms of the cell membrane,reaching the nucleus of the cell, initiating a transcription process that controls the production and abundance of proteins. Proper functioning of these networks is essential to the survival and adapation of all living organisms, while malfunctioning of these networks has been identified as the cause of various diseases \citep{An evaluation of methods for inferring boolean network from time-series data}.
To understand the behaviour of a biological system it is necessary to find and analyze the main important processes in a system in a dynamical manner. Therefore high-throughput techniques provide a big abundance of information about various biological interactions measured over a series of time. Biological information can be considered as different systems such as signal transduction, gene regulation, protein-protein-interaction or metabolism. These information are put in a network which can be yielded by several strategies like Baysian networks, Boolean regulatory networks, Ordinary differential equation models and Neural networks\citep{SAADATPOUR20133}.Once a network is constructed further anaylsis of the network by validating the network (e.g. pertubations like gene manipulation and external treatments, reductions etc.)can be done to figure out the main interactions whose disfunctionalities cause diseases.
This masterthesis focuses on constructing a pipeline by creating a boolean network from a real-life time course data set.
In the following section the biological background of data, it's preprocessing by normalization and descretization,the graphtheoretical background and scoring methods are described.
In the second section it is getting more detailed by giving an overview of different inference algorithms, describing a tool called PyBoolNet and showing with an example data set and a real-life time course data set of breast cancer celllines how the pipeline is applied.
In the last section the scoring results for the real-life time course data set are analyzed reflecting the peformance of the constructed network.


